\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-11 paper/main.tex
writing in third person

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
based on the kind of build, and column ``environment'' shows the
breakdown of instances based on the kind of environment we use to
reproduce the bug.

>>>>

\tname\ contains \numbugs{} instances of reproducible bugs
representing three popular DL libraries, namely, \jax, \tf, and
\torch. Table~\ref{table:bug-characterization} shows the list of bug
instances for each supported library. Column ``\#'' shows the number
of bug instances, column ``build'' shows the breakdown of instances
based on the kind of build, and column ``environment'' shows the
breakdown of instances based on the kind of environment to reproduce
the bug.
